\documentclass{article}
\usepackage{pgfplotstable}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{siunitx}
\pgfplotsset{compat=newest}

\begin{document}
\begin{table}[h!]
	\centering
	\caption{Does an individual make $<50$k?}
    \pgfplotstabletypeset[
        col sep=comma,
	columns={size,action,r1,metric,r2,value},
        columns/size/.style = {
            string type, column name = Model Size},
        columns/action/.style = {
            string type, column name = Fairness Action},
	columns/metric/.style = {
            string type, column name = Race},
        columns/r1/.style = {
            string type, column name = Metric},
	columns/r2/.style = {
            string type, column name = Over Race},
        columns/value/.style = {
            column name = Metric Value},
        every head row/.style={
            before row={\toprule},
	},
        every last row/.style={after
        row=\bottomrule}]{results.csv}
\end{table}

We use several neural network models to determine if an individual
makes over $50k$.
We make the following observations to helpe ase the reading of the table.
\begin{itemize}
	\item For the small model with no fairness action,
		black's advantage over white is $0.29$. This means
		if $t_1$ is the proportion of black individuals who
		are judge to make $<50$k by the model,
		and $t_2$ is the proportion of black individuals who
		are also judge to make $<50$k using the white
		criteria, $t_1 - t_2 = 0.29$. Out of all the black
		population, 29\% of them would have not been judge to
		make $<50$k if they had been white.
	\item For the small model with no fairness action, the
		model's preference for black features over white is
		$0.39$. If $t_1$ is the proportion of black
		individuals judge to make $<50$k by the
		model, and $t_2$ is the proportion of white
		individuals judge to make  $<50$k by the
		model using the black criteria, $t_1 - t_2=0.39$.
	\item For the small model with no fairness action,
		white's advantage over black is $0\approx
		\num{-5.55e-17}$. This means there is no
		white individual that the model judged to make
		$<50$k who would also not have not received
		the same judgement if they were black.
	\item We see that there is no difference in the preference and
		advantage compared to no fairness action for either races when
		the sex is permuted, which is expected. However, when we assign
		to race and random weight, there is still no difference  in the
		preferences and advantage compared to no fairness action for
		either races, which is unexpected. Perhaps there is a mistake
		in the model?
	\item For the medium-sized model, it seems that permuting the race
		makes it much more likely to thing that Blacks earn less. This
		is suprising as when no fairness action, neither race had a
		very strong advantage or preference.
\end{itemize}

\end{document}

